Supporting information: Copulas and their potential for ecology

### 2019-10-07 Paper.Rmd
table fixed

<!--***DAN: Shyamolina, can you please move what is currently Table S10 (Summary results
for winter temp and green spruce aphid abundance) to here? Please also replace the two
columns that show AICw values by the corresponding AIC values, consistent with the switches
elsewhere in the paper of AICw for AIC.-->

>>>>

```{r tab_greenspruceaphid_temp_summary, echo=F, results='asis',message=F}
library(kableExtra)
ms_npa_RES_greenspruceaphid_count_temp<-readRDS("./Results/aphid_count_winter_temp_results/ms_npa_RES_greenspruceaphid_count_temp.RDS")
res<-ms_npa_RES_greenspruceaphid_count_temp$sp10_Green_spruce_aphid$ms_summary_allloc
#row.names(res)<-NULL
#res<-cbind(c(2:11),res)
colnames(res)<-c("p-value, independence test","Best-fit copula",
                 "Best-fit AIC","Normal AIC","p, CvM","p, KS","Model-avg. LT","Model-avg. UT","Model-avg. LT minus UT","cor$_{l}$ - cor$_{u}$","P$_{l}$ - P$_{u}$","D$_{u}^2$ - D$_{l}^2$")
res<-res[,-1]
res<-cbind("Site"=c(2:11),res)
knitr::kable(res,"latex", booktabs = T, linesep = "",digits=3, escape=F,longtable=T,row.names = F,
             caption.short="Summary results for copulas for winter temperature versus green spruce aphid abundance",
      caption = "Summary results for analysis of copulas for winter temperature versus green spruce 
aphid abundance for each of the 10 sampling locations, using the same model selection
and nonparametric methods detailed in the section on methods for Q1. The column labeled p, CvM is the p-value 
result for the goodness of fit test using the Cramer-von Mises statistic. The 
column labeled p, KS is the p-value 
result for the goodness of fit test using the Kolmogorov-Smirnov statistic. Entries with an NA are because model selection and other statistics
were only employed for copulas for which independence was rejected (5 percent significance level).\\label{tab:greenspruce}") %>% column_spec(1:12,width="1.1 cm")#%>%
#kable_styling(latex_options = c("scale_down"))
```

### 2019-10-07 SupportingInformation.Rmd
table fixed

    m<-as.data.frame(matrix(NA,1,12))
    colnames(m)<-c("p.Indep","minAIC.bestfit.cop","Bestfit.cop.AICw",
                   "Normal.cop.AICw","p.CvM","p.KS",
                   "LT.model.avg","UT.model.avg","(LT-UT).model.avg",
                   "CorlmCoru","PlmPu","D2umD2l")
    m$p.Indep<-ms_res$IndepTestRes

@@

      m$minAIC.bestfit.cop<-ms_res$InfCritRes$copname[which.min(ms_res$InfCritRes$AIC)]
      m$Bestfit.cop.AICw<-round(max(ms_res$InfCritRes$AICw),3)
      m$Normal.cop.AICw<-round(ms_res$InfCritRes$AICw[1],3)
      m$p.CvM<-ms_res$GofRes_CvM
      m$p.KS<-ms_res$GofRes_KS
      m$LT.model.avg<-round(ms_res$relLTdep_AICw,3)
      m$UT.model.avg<-round(ms_res$relUTdep_AICw,3)
      m$`(LT-UT).model.avg`<-m$LT.model.avg-m$UT.model.avg
      m$CorlmCoru<-CorlmCoru
      m$PlmPu<-PlmPu
      m$D2umD2l<-D2umD2l
    }

@@

```{r tab_greenspruceaphid_temp_summary, echo=F, results='asis',message=F}
library(kableExtra)
set.seed(seed)

res<-ms_npa_RES_greenspruceaphid_count_temp$sp10_Green_spruce_aphid$ms_summary_allloc
#row.names(res)<-NULL
#res<-cbind(c(2:11),res)
colnames(res)<-c("p-value, independence test","Best-fit copula",
                 "Best-fit copula AICw","Normal copula AICw","p, CvM","p, KS","Model-avg. LT","Model-avg. UT","Model-avg. LT minus UT","cor$_{l}$ - cor$_{u}$","P$_{l}$ - P$_{u}$","D$_{u}^2$ - D$_{l}^2$")
res<-res[,-1]
knitr::kable(res,"latex", booktabs = T, linesep = "",digits=3, escape=F,longtable=T,
             caption.short="Summary results for copulas for winter temperature versus green spruce aphid abundance",
      caption = "Summary results for analysis of copulas for winter temperature versus green spruce 
aphid abundance for each of the 10 sampling locations, using the same model selection
and nonparametric methods detailed in the section on methods for Q1. The column labeled p, CvM is the p-value 
result for the goodness of fit test using the Cramer-von Mises statistic. The 
column labeled p, KS is the p-value 
result for the goodness of fit test using the Kolmogorov-Smirnov statistic. Entries with an NA are because model selection and other statistics
were only employed for copulas for which independence was rejected (5 percent significance level).\\label{tab:greenspruce}") %>% column_spec(1:12,width="1.2 cm")#%>%
#kable_styling(latex_options = c("scale_down"))
```

>>>>

    m<-as.data.frame(matrix(NA,1,12))
    colnames(m)<-c("p.Indep","minAIC.bestfit.cop",
                   "Bestfit.cop.AIC", "Normal.cop.AIC",
                   "p.CvM","p.KS",
                   "LT.model.avg","UT.model.avg","(LT-UT).model.avg",
                   "CorlmCoru","PlmPu","D2umD2l")
    m$p.Indep<-ms_res$IndepTestRes

@@

      m$minAIC.bestfit.cop<-ms_res$InfCritRes$copname[which.min(ms_res$InfCritRes$AIC)]

      m$Bestfit.cop.AIC<-round(min(ms_res$InfCritRes$AIC),3)
      m$Normal.cop.AIC<-round(ms_res$InfCritRes$AIC[1],3)

      m$p.CvM<-ms_res$GofRes_CvM
      m$p.KS<-ms_res$GofRes_KS
      m$LT.model.avg<-round(ms_res$relLTdep_AICw,3)
      m$UT.model.avg<-round(ms_res$relUTdep_AICw,3)
      m$`(LT-UT).model.avg`<-m$LT.model.avg-m$UT.model.avg
      m$CorlmCoru<-CorlmCoru
      m$PlmPu<-PlmPu
      m$D2umD2l<-D2umD2l
    }

@@
